I want to express my deepest gratitude to my advisor, 
Dr. Kathryn Huff, for her guidance, patience, and 
support in my learning journey towards becoming a proper scientist.
I also wish to thank Dr. Bo Feng from Argonne National 
Laboratory for his guidance and direction in conducting 
sensitivity analysis studies and invaluable career advice.  
I would also like to acknowledge Dr. James Stubbins as the 
second reader of this thesis; I am grateful for his valuable 
comments on this thesis. 
This work would not have been possible without the 
financial support of the Nuclear Energy University Program 
for funding me through (Project 16-10512, DE-NE0008567) 
`Demand-Driven Cycamore Archetypes'.

I thank my fellow groupmates, for the embodiment of `misery 
loves company', Greg Westphal, Jin Whan Bae, Sun Myung Park, 
Roberto Fairhurst, Anshuman Chaube, Kip Kleimenhagen, 
Gyu Tae Park, Andrei Rykhlevskii, and Sam Dotson. 
Special thanks to Kip Kleimenhagen for his excellent proofreading. 
I also had the pleasure of collaborating with the wonderful 
and supportive Cyclus community, particularly those in the 
University of Wisconsin \gls{CNERG} and the University of 
South Carolina Energy Research Group (ERGS). 
I am also grateful to my WiN family for my weekly dose 
of good vibes and rapport. 
Special thanks to my roommate, Mao, who always brightened my 
day with baked goods and funny memes. 

Finally, I cannot begin to express my thanks to my parents, 
Joy and Gerard, and my brother, Ben, for their unwavering love 
and support from day one. 

