\chapter[Introduction]{Introduction}
\label{chap:1}

\section{Motivation}
The impact of climate change on natural and human systems 
is increasingly apparent \cite{noauthor_climate_2018}.
Increases in global average 
surface temperatures, sea levels, and larger climate extremes
are a few consequences brought on by elevated \gls{GHG} 
concentrations \cite{noauthor_climate_2018}.
Energy use and production contribute to 
two-thirds of the total \gls{GHG}
emissions \cite{noauthor_climate_2018}.
Furthermore, as the human population increases and previously 
under-developed nations rapidly urbanize, 
global energy demand is forecasted to increase.  
Energy generation technology selection 
profoundly impacts climate change via growing energy demand. 
Large scale deployment of emissions free nuclear power plants 
could significantly reduce GHG production 
\cite{noauthor_climate_2018}.  

However, large scale nuclear power deployment faces
challenges of cost, safety, and used nuclear fuel  
\cite{petti_future_2018}. 
Nuclear power has high capital costs, 
an unresolved long-term nuclear waste management 
strategy and perceived adverse safety, environmental, and health 
effects \cite{petti_future_2018}. 
The nuclear power industry must overcome these challenges 
to ensure continued global use and expansion 
of nuclear energy technology. 

The challenges described above are associated with 
the present once-through fuel cycle in the \gls{US}, 
in which fabricated nuclear fuel is used once and placed into 
storage to await disposal. 
To overcome these challenges, the national laboratories 
use nuclear fuel cycle simulators to explore 
long-term behavior and performance of alternative fuel cycles. 
Nuclear fuel cycle simulators are used to evaluate the impact of 
nuclear fuel cycles at both high and low resolution. 
These simulators track the flow of materials through the nuclear fuel cycle, 
from enrichment to final disposal of the fuel, while also accounting for 
decay and transmutation of isotopes. 
By evaluating performance metrics of different fuel cycles, we gain an 
understanding of how each facility's parameters and technology choices 
impact the system's performance. 
Therefore, these results are used by DOE to inform research direction
and funding decisions, and advise future reactor design choices 
\cite{yacout_modeling_2005}.

The Office of Nuclear Energy's
\gls{FCO} Campaign led an evaluation 
sand screening study of a comprehensive set of nuclear \glspl{FCO} 
to identify \glspl{FCO} with the potential to substantially 
improve the nuclear fuel cycle in the challenge areas
\cite{wigeland_nuclear_2014}. 
The study concluded that fuel cycles with continuous recycling
of co-extracted U/Pu or U/TRU in fast spectrum critical reactors
consistently scored high overall performance in the following 
categories: used nuclear fuel management, environmental impact, 
and resource utilization. 
The evaluation and screening study assumed
the nuclear energy systems were at equilibrium to understand 
each Evaluation Group's
end-state benefits \cite{feng_standardized_2016}. 
Therefore, evaluation of the transition from the current 
once-through fuel cycle to these promising 
future end-states \cite{feng_standardized_2016} 
is the logical next step, propelling this
nuclear fuel cycle transition scenario analysis research. 

Nuclear fuel cycle simulation tools must automate the transition scenario simulation 
setup to successfully model a time-dependent transition scenario. 
Many existing nuclear fuel cycle simulator tools have conducted 
transition scenario analyses 
\cite{feng_standardized_2016,bae_standardized_2019,coquelet-pascal_cosi6:_2015}
and faced challenges stemming from the vast input parameter
sample space.
Since many of these input parameters are coupled, it is 
a tedious process to use trial and error to manually find a balance 
between various input parameters to set up a successful transition 
scenario. 
We define a successful transition scenario simulation as one that 
has a minimal power undersupply, minimal undersupply, 
and oversupply of all commodities. 
 
In reality, the real transition process inevitably diverges
from the modeled transition scenario. 
It is insufficient to set up only one transition scenario to model 
nuclear power's future projections.
Therefore, it is imperative to conduct sensitivity analysis to understand 
the effect of variation in input parameters on 
performance metrics. 

\section{Objectives}
This thesis' objectives were developed based on the difficulties 
nuclear fuel cycle simulators face when modeling transition scenarios 
and conducting sensitivity analysis in the context of those scenarios.
Accordingly, the objectives are listed below. 
\paragraph{Develop a capability in \Cyclus to ease the setup of 
transition scenarios.}
Due to the interdependence of many nuclear fuel cycle input parameters, 
nuclear fuel cycle simulator users'
must manually determine each facility's deployment schedule 
to avoid supply chain gaps. 
Thus, a next-generation nuclear fuel cycle simulator must automate 
transition scenario setup by predictively and 
automatically deploying fuel cycle facilities to meet user-defined 
power demand. 

\paragraph{Develop sensitivity analysis capabilities in \Cyclus and DYMOND.}
Sensitivity analysis identifies areas in the nuclear fuel cycle
that highly influence performance metrics. 
We leverage Dakota \cite{eldred_dakota_2010}, a well supported sensitivity 
analysis tool, to introduce sensitivity analysis capabilities to 
\Cyclus and DYMOND.  

\paragraph{Demonstrate \Cyclus transition scenario setup using the 
developed capability.} 
We demonstrate successful implementation of \Cyclus' automated transition scenario 
setup capability by setting up a simple three-facility transition scenario and 
a complex closed fuel cycle transition scenario. 

\paragraph{Use \Cyclus and DYMOND to conduct sensitivity studies.}
We demonstrate one-at-a-time, synergistic, and global sensitivity analysis 
with \Cyclus-Dakota and DYMOND-Dakota. 

\paragraph{Compare \Cyclus-Dakota's and DYMOND-Dakota's capabilities in conducting sensitivity 
analysis.} 
DYMOND lacks the automated transition scenario setup capability that was developed for 
\Cyclus. 
Through comparison of sensitivity analysis studies conducted by \Cyclus-Dakota and 
DYMOND-Dakota, we demonstrate the importance of automated transition scenario setup 
capability in nuclear fuel cycle simulators. 


